### 2024-02-04 README.Rmd
change intro of readme

The goal of sfislands is to ...

@@

@@

## Summary

1.  `sfislands` makes it easier to deal with geographic datasets which contain islands. These do not have to be "literal" islands but any situation where one or more discontiguous geographical unit is present. Such a situation can lead to two issues. Firstly, if unaddressed, the presence of such islands or exclaves can make certain types of contiguity-based modelling impossible. Secondly, just because two areas are separated by, say, a body of water, this does not mean that they are necessarily independent. The package offers solutions to allow for the inclusion or exclusion of these units within an uncomplicated workflow.

2.  As an aid to this, the package also has a function to quickly map any contiguity structure for visual inspection. This can also be used to examine the output of `sfdep` contiguity functions. This can be used to check if the structure makes sense, given the researcher's knowledge about the geography of the study area.

3.  If there are some contiguities present which are not appropriate, or if you wish to add additional ones, there are functions to allow this to be done in a straightforward and openly reportable way.

4.  Once an appropriate neighbourhood structure is in place, different types of statistical tests and models can be performed. `sfdep` contains functionality to perform such test, and the output from `sfislands` can be used in its functions.

5.  The contiguity outputs from `sfislands` can be directly used to fit different types of (multilevel) (I)CAR models using, for example, the `mgcv`, `brms`, `stan` or `INLA` packages.

6.  For `mgcv` in particular, the predictions of such models can be quite tedious to extract and visualise. `sfislands` can streamline this workflow from the human side. Furthermore, there is a function to draw maps of these predictions for quick inspection.

>>>>

The goal of `sfislands` is to make it easier to deal with geographic datasets which contain islands. These do not have to be "literal" islands but any situation where one or more discontiguous geographical units are present. Such a situation can lead to two issues. Firstly, if unaddressed, the presence of such islands or exclaves can make certain types of contiguity-based modelling impossible. Secondly, just because two areas are separated by, say, a body of water, this does not mean that they are necessarily independent. The package offers solutions to allow for the inclusion or exclusion of these units within an uncomplicated workflow.

@@

## Summary of features

1.  As an aid to setting up contiguity structures, particularly when islands are involved, the package has a function to quickly map any contiguity structure for visual inspection. This can also be used to examine the output of `sfdep` contiguity functions. Such maps can be used to check if the structure makes sense, given the researcher's knowledge about the geography of the study area.

2.  If there are some contiguities present which are not appropriate, or if you wish to add additional ones, there are functions to allow this to be done in a straightforward and openly reportable way.

3.  Once an appropriate neighbourhood structure is in place, different types of statistical tests and models can be performed. `sfdep` contains functionality to perform such test, and the output from `sfislands` can be used in its functions.

4.  The contiguity outputs from `sfislands` can be directly used to fit different types of (multilevel) (I)CAR models using, for example, the `mgcv`, `brms`, `stan` or `INLA` packages.

5.  For `mgcv` in particular, the predictions of such models can be quite tedious to extract and visualise. `sfislands` can streamline this workflow from the human side. Furthermore, there is a function to draw maps of these predictions for quick inspection.

@@
